\section{ARIFI's project description}
ARIFI is an ongoing project whose main goal is to combine GNSS services with Artificial intelligence into a web application. This application will provide agricultors not only with useful data, but also with instructions on what actions to take so as to manage more efficiently their farms and improve their harvest profits.\\
%
%
The project started after a several discussions with farmers from different countries around the world. The intention of this conversations via phone calls or e-mail, was to get a deeper insight on the current agriculture situation. We tried to analyse common difficulties among farmers, despite being far apart from one another, making special emphasis in those that we thought we contribute to, as a team with solid knowledge in GNSS and AI.\\
%
%
In conclusion, we obtained valuable feedback from farmers that helped the team to better shape the project and define more clearly which difficulties we wanted to adress with ARIFI. The later have been itemized and briefly described next, so as to give a more schematic look of what we concluded.
% REVISAAAAAAAAAAAAAAR JOAN
%::::::::::::::::::
%::::::::::::::::::
%::::::::::::::::::
\begin{itemize}
    \item \textbf{Interpretation of weather forecasts:} It is well known that weather forecasts are of extreme importance for agriculture. It helps farmers to prevent their harvest to be damaged and also to adapt system such as irrigation. In this case, we found that the forecasts most farmers obtained were not detailed enough in many cases, and more importantly, most of them were only useful for well experienced agricultors which knew to interpret this information and what actions to take in result. This is a problem that ARIFI wants to solve by gathering all the necessary data, not only to make weather forecasts, but also to combine it with data from other sources so as to provide users with instructions on how to act even if they are not well experienced farmers. This can be specially useful in the agriculture sector from developing countries that lack from technical advise from specialized companies. 
    \item \textbf{knowledge of field's characteristics:} Although all farmers know their fields to some extend, not many have detailed knowledge about aspects, e.g. soil height irregularities, chemical characteristics etc, which are relevant for many farming activities. This characteristics are currently not easy to determine and in some cases it implies expensive measurings processes that might take long. In this aspect ARIFI wants to provide with useful information by processing copernicu's images.
    \item \textbf{Adaptation to climate change:}
\end{itemize}

\input{overview}
\newpage
\subsection{Technical aspect}
\subsubsection{GNSS side}
\begin{itemize}
    \item \textbf{GALILEO}
    \item \textbf{EGNOS}
    \item \textbf{Copernicus}
\end{itemize}
\subsubsection{AI side}
To address the proposed idea and achieve our goal, we will focus on how to relate machine learning techniques, field of Artificial Intelligence (AI), with the study of the atmosphere provided by satellite data. Thanks to the Copernicus Atmosphere Monitoring Service, we will be able to access to data that will allow us to predict the main atmospheric phenomenons which affects the production of the majority farmers.\\\\
%
In particular, we are talking about reanalysis variables. This kind of data is obtained by some weather forecasting centres, which combine past observations with a modern meteorological forecast model, in order to produce regular gridded datasets of many atmospheric and oceanic variables, with a temporal resolution of a few hours. This datasets usually extend over several decades and cover the entire planet, being a very useful tool for meteorological and climatological studies.\\\\
%
One of the most important reanalysis projects is the {\em ERA-Interim reanalysis project}, produced by the European Centre for Medium-Range Weather Forecasts (ECMWF) \cite{ERA_Interim}, which belongs to the Copernicus Programme. ERA-Interim is a global atmospheric reanalysis from 1979, continuously updated in real time.\\\\
%
Table \ref{Variables_ERA} is just an example of variables that can be obtained from this platform, which could be used as predictors in machine learning models.

\vspace{12pt}
\begin{table}[H]
\begin{center}
\caption{\label{Variables_ERA} Possible predictive variables in a prediction problem.}
\begin{tabular}{cccc}
\hline
variable name & ERA-Interim variable\\
\hline
\hline
skt & surface temperature\\
sp & surface pression\\
$u_{10}$& zonal wind component ($u$) at 10m\\
$v_{10}$& meridional wind component ($v$) at 10m\\
temp1& Temperature at 500hPa\\
up1& zonal wind component ($u$) at 500hPa\\
\hline
\end{tabular}
\end{center}
\end{table}
\vspace{12pt}

Due to the chaotic nature of atmospheric phenomenons it is so difficult predict with precision its future state. Modeling it without any un- certainty is not possible as there is a strong sensitivity to small perturbations in the initial conditions. But there is a way to overcome this issue by the use of probabilistic weather forecasts \cite{martinez2015forecasting}. In this regard, we propose computational methods belonging to machine learning techniques, a branch of AI, to get predictions or classifications over the main atmospheric factors with high accuracy. We could predict solar radiation, wind velocity, or whatever meteorological process that injures in the farmers' environment. Of course, it would not be possible without GNSS services that provide the essential dataset, as we mentioned before, necessary to train the learning models.

Many of these methods can be classified in the field of Knowledge called “Natural Computing”. The algorithms that can be found in this category are inspired by the way Nature solves complex problems. In this regard, Evolutionary Computation (EC) is inspired in the theory of evolution or Artificial Neural Networks (ANN) find their behaviour in human brain.

The conjunction between satellite data and machine learning algorithms will allow us to provide solutions to those aspects that most concern farmers, in order to keep their harvests safe with the highest possible productivity. For instance, if we are able to anticipate how much water they will have at a given time, or to warn of a dry season that was not previously contemplated but, due to the effects produced by climate change may occur, we will have a positive influence on their economy by avoiding unnecessary expenses derived from poor management, because they do not have all the information they could.

\subsection{Added value}
\subsubsection{Comparisons}	
\subsection{Discussion of critical areas}
