
\begin{thebibliography}{100}

\bibitem{ERA_Interim}
Dick~P Dee, SM~Uppala, AJ~Simmons, Paul Berrisford, P~Poli, S~Kobayashi,
  U~Andrae, MA~Balmaseda, G~Balsamo, P~Bauer, et~al.
\newblock {The ERA-Interim reanalysis: Configuration and performance of the
  data assimilation system}.
\newblock {\em Quarterly Journal of the royal meteorological society},
  137(656):553--597, 2011.

\bibitem{martinez2015forecasting}
G~Mart{\'\i}nez-Arellano.
\newblock {\em Forecasting wind power for the day-ahead market using numerical
  weather prediction models and computational intelligence techniques}.
\newblock PhD thesis, Nottingham Trent University, 2015.

\bibitem{galileo}
Navipedia
\newblock {\em 	Galileo General Introduction}.
\newblock \link{https://gssc.esa.int/navipedia}

\bibitem{egnos}
Navipedia
\newblock {\em 	EGNOS General Introduction}.
\newblock \link{https://gssc.esa.int/navipedia}

\bibitem{cop_atm}
European's comission. \em{Copernicus factsheets} \\\link{https://www.copernicus.eu/en}

\bibitem{Gal_pos}
Weiwang Wu, Fei Guo and Jiazhu Zheng 
\newblock {Analysis of Galileo signal-in-space range error and positioning performance during 2015–2018}.
\newblock {\em Satellite Navigation}, 1, 6, 2020.

\bibitem{Himalaya}
\newblock {HIgh performance MAss market GNSS receiver muLti stAndard readY for mArket (HIMALAYA)}.
\newblock {\em FP7-TRANSPORT}.

\bibitem{PPP}
Kouba J., Lahaye F., Tétreault P.
\newblock {Precise Point Positioning. In: Teunissen P.J., Montenbruck O. (eds) Springer Handbook of Global Navigation Satellite Systems}.
\newblock {\em Springer Handbooks. Springer, Cham}, 2017.

\bibitem{RTK1}
Rietdorf, A., Daub, C., & Loef, P. 
\newblock {Precise Positioning in Real-Time using Navigation Satellites and Telecommunication}.
\newblock {\em In Proceedings of The 3rd Workshop on Positioning and Communication (WPNC’06)}, 2006.

\bibitem{RTK2}
Odijk D., Wanninger L.
\newblock {Differential Positioning. In: Teunissen P.J., Montenbruck O. (eds) Springer Handbook of Global Navigation Satellite Systems}.
\newblock {\em Springer Handbooks. Springer, Cham}, 2017.

\end{thebibliography}
